\ttitle

### 2013-11-14 Chapters/Chapter4/change_detection.tex
Add caption titles to tables

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  1 & Start with $n$ data objects as working set and construct hypersphere \\
  2 & Add next data object $x_t$ and drop first one \\
  3 & Identify new hyper-sphere and its \emph{approximate radius} \\
  4 & calculate radius average of hyperspheres since last change point \\
  5 & calculate radius ratio $\hbar$. If lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point \\
  6 & continue from step 2, until no more data objects available \\
  7 & Apply post-processing: merge close change points \\
  \hline
\end{tabular}
\caption{Algorithm of the proposed change detection method, using the Ratio-Thresholding method of \ref{subsec:ratio_thresholding} for change detection.}
\label{tab:algorithm_proposed_method}
\end{table}\end{center}

>>>>

\begin{center}\begin{table}
\begin{tabular}{ l p{12cm} }
  \hline
  Step & Action \\
  \hline
  1 & Start with $n$ data objects as working set and construct hypersphere \\
  2 & Add next data object $x_t$ and drop first one \\
  3 & Identify new hyper-sphere and its \emph{approximate radius} \\
  4 & calculate radius average of hyperspheres since last change point \\
  5 & calculate radius ratio $\hbar$. If lower than ${th}_{low}$ or greater than ${th}_{high}$ then mark $t$ as change point \\
  6 & continue from step 2, until no more data objects available \\
  7 & Apply post-processing: merge close change points \\
  \hline
\end{tabular}
\caption[Proposed algorithm]{Algorithm of the proposed change detection method, using the Ratio-Thresholding method of \ref{subsec:ratio_thresholding} for change detection.}
\label{tab:algorithm_proposed_method}
\end{table}\end{center}
